Enrich the datasets with new columns.

### 2020-08-21 inst/analysis/enrich_dataset.Rmd
Right eval_call_package

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
eval_calls_dedup <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
eval_calls_dedup_more <- eval_calls %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
```

```{r}
eval_calls <- eval_calls_dedup_more %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

@@

>>>>

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_ev_calls") 
eval_calls_dedup <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
eval_calls_dedup_more <- eval_calls %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_ev_calls") 
```

```{r}
eval_calls_dedup_more <- eval_calls_dedup_more %>% mutate(parse_args = map(expr_parsed_expression, function(e) { if(!is.na(e) && str_starts(e, "(parse|str2lang|str2expression)\\("))   extract_args_parse(e) else list() }))  %>% unnest_wider(parse_args)
```

@@

```{r}
eval_calls <- eval_calls %>% select(-ends_with("_type")) %>% left_join(eval_calls_dedup_more)
eval_calls_dedup <- eval_calls_dedup %>% select(-ends_with("_type"))%>% left_join(eval_calls_dedup_more)
```
